---
title: "Spaceship Titanic"
author: "Yuxi Wang"
date: '2022-04-01'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spaceship Titanic

The Spaceship Titanic was an interstellar passenger liner launched a month ago. With almost 13,000 passengers on board, the vessel set out on its maiden voyage transporting emigrants from our solar system to three newly habitable exoplanets orbiting nearby stars.

While rounding Alpha Centauri en route to its first destination—the torrid 55 Cancri E—the unwary Spaceship Titanic collided with a spacetime anomaly hidden within a dust cloud. Sadly, it met a similar fate as its namesake from 1000 years before. Though the ship stayed intact, almost *half* of the passengers were transported to an alternate dimension!

To help rescue crews and retrieve the lost passengers, there is a need to predict which passengers were transported by the anomaly using records recovered from the spaceship’s damaged computer system.

```{r packages,echo = FALSE,message=FALSE}
#packages: ggplot2, tibble, tidyr, readr,purrr,dplyr,stringr,forcats
if (!require("tidyverse")){
  install.packages("tidyverse")
  library("tidyverse")
}
#packages: htmlwidgets,igraph,gridExtra,networkD3,DataExplorer
if (!require("DataExplorer")){
  install.packages("DataExplorer")
  library("DataExplorer")
}

if (!require("ggcorrplot")){
  install.packages("ggcorrplot")
  library("ggcorrplot")
}

```

### Read Data

```{r data,message=FALSE}
train<-read_csv("data/train.csv", col_names = TRUE)
test<-read_csv("data/test.csv", col_names = TRUE)
```

#EDA
```{r EDA.test, echo=FALSE}
plot_histogram(train)
plot_boxplot(train, by = "Transported")
library(ggcorrplot)

```

### Data Wrangling and Cleaning

```{r dataWrgl}
train<-train %>% 
  separate(PassengerId,c("Passenger_Group","Passenger_GroupNum"),
           remove = FALSE) %>% 
  separate(Cabin,c("Cabin_deck","Cabin_num","Cabin_side"),remove = FALSE)
```

```{r dataCln}
#DATA CLEANING

##removing unwanted observations-duplicate or irrelevant
###check with duplicate records
length(unique(train$PassengerId))==length(train$PassengerId) #no duplicates

#find columns with NAs
names(which(colSums(is.na(train))>0))
```
